Approximation as Differentiation

### 2025-05-06 appendix/notes/auto-diff-galois-slicing-via-fam.tex
Clarify \partial f is family of Galois connections.

$\Fam(\LatGal)$ has:
\begin{itemize}
\item as objects $(X, \partial X)$ all pairs of a set $X$ and and for each $x \in X$, a bounded lattice
$\partial X_x$;
\item as morphisms $(X, \partial X) \to (Y, \partial Y)$, all pairs $(f, \partial f)$ of functions $f: X \to
Y$ and Galois connections $\partial f: \partial X_x \to \partial Y_{f(x)}$.
\end{itemize}

>>>>

$\Fam(\LatGal)$ has:
\begin{itemize}
\item as objects $(X, \partial X)$ all pairs of a set $X$ and and for every $x \in X$, a bounded lattice
$\partial X_x$;
\item as morphisms $(X, \partial X) \to (Y, \partial Y)$, all pairs $(f, \partial f)$ of functions $f: X \to
Y$ and families of Galois connections $\partial f_x: \partial X_x \to \partial Y_{f(x)}$ for every $x \in X$.
\end{itemize}

\noindent with the role of the pullback along $f$ in the composition $(g, \partial g) \comp (f, \partial f) =
(g \comp f, \reindex{\partial g}{f} \comp \partial f)$ being to select the appropriate lattice of
approximations and Galois connection at each point.
